RJObject Paper

### 2014-06-19 Documents/Paper/ms.tex
Talking about the simulated sinewave data

The model for the signal is
\begin{eqnarray}
\mu(t) &=& \sum_{i=1}^N A_i \sin \left(\frac{2\pi t}{T_i} + \phi_i\right)
\end{eqnarray}
where there are $N$ sinusoids in the signal, the
amplitudes are $\{A_i\}$, the periods are $\{T_i\}$, and the phases are
$\{\phi_i\}$.

The sampling distribution (probability distribution for the data given the
parameters) is a normal (gaussian) distribution with mean zero and standard
deviation $\sigma$, applied independently to each data point:
\begin{eqnarray}
y_i | N, \{A_i\}, \{T_i\}, \{\phi_i\} \sim
\mathcal{N}\left(\mu(t_i), \sigma^2\right).
\end{eqnarray}
We simulated some data based on the assumption $N=2$.
The simulated data is shown in Figure~\ref{fig:sinewave_data}, and shows a
large, low period oscillation with a smaller, much faster oscillation
superimposed. The noise level is such that the fast oscillation is difficult
to detect.

The true values of the parameters are $N=2$, $\mathbf{A} = \{1, 0.3\}$,
$\mathbf{T}=\{30, 2\}$, and $\boldsymbol{\phi} = \{0, 1\}$. The signal was
observed at $n=1001$ points equally spaced between $t=0$ and $t=100$. The data
is displayed in Figure~\ref{fig:sinewave_data}.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewave_data.pdf}
\caption{The simulated data for the sinusoidal example.
\label{fig:sinewave_data}}
\end{center}
\end{figure}

%\section{``Transit'' example}

>>>>

The model for the signal is
\begin{eqnarray}
y(t) &=& \sum_{i=1}^N A_i \sin \left(\frac{2\pi t}{T_i} + \phi_i\right)
\end{eqnarray}
where there are $N$ sinusoids in the signal, the
amplitudes are $\{A_i\}$, the periods are $\{T_i\}$, and the phases are
$\{\phi_i\}$.

The sampling distribution (probability distribution for the data given the
parameters) is a normal (gaussian) distribution with mean zero and standard
deviation $\sigma$, applied independently to each data point:
\begin{eqnarray}
Y_i | N, \{A_i\}, \{T_i\}, \{\phi_i\} \sim
\mathcal{N}\left(\mu(t_i), \sigma^2\right).
\end{eqnarray}
We simulated some data based on the assumption $N=2$.
The simulated data is shown in Figure~\ref{fig:sinewave_data}, and shows a
large, low period oscillation with a smaller, much faster oscillation
superimposed. The noise level is such that the fast oscillation is difficult
to detect. The true values of the parameters were
$N=2$, $\mathbf{A} = \{1, 0.3\}$,
$\mathbf{T}=\{30, 2\}$, and $\boldsymbol{\phi} = \{0, 1\}$. The signal was
observed at $n=1001$ points equally spaced between $t=0$ and $t=100$.
The true form of the signal is:
\begin{eqnarray}
y(t) = \sin\left(\frac{2\pi t}{30}\right) +
0.3 \sin\left(\frac{2\pi t}{2} + 1\right)
\end{eqnarray}
and the noise standard deviation was $\sigma = 1$. The data $\{Y_i\}_{i=1}^n$
is displayed in Figure~\ref{fig:sinewave_data}.

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{sinewave_data.pdf}
\caption{The simulated data for the sinusoidal example. The solid line shows
the true signal and the points are the measurements, simulated based on a
noise standard deviation of $\sigma = 1$.
\label{fig:sinewave_data}}
\end{center}
\end{figure}

%\section{``Transit'' Example}
%\section{``Asteroseismology'' Example}
%\section{``Galaxy Field'' Example}
%\section{``Transit'' example}
